\vspace{-2.0em}
\cvsection{Working Experience}
\begin{cventries}
    \cventry
    {Senior Blockchain Engineer - Protocol}
    {ChainSafe Systems - \href{https://github.com/ChainSafe/gossamer}{Gossamer}(Polkadot Go Implementation)}
    {Global}
    {Feb. 2025 - Now}
    {
      \begin{cvitems}
        \item {Tech Stack: Rust, Go, Polkadot, Libp2p, Kademlia DHT, Concurrency, Distributed message gossip system}
        \item {Delivered core components of a full blockchain node, partnering with protocol, runtime, and networking teams to implement consensus, P2P systems, and state-machine logic.}
        \item {Took lead ownership of backend subsystems supporting block production and candidate lifecycle workflows, driving design, architecture, and high-quality implementation.}
        \item {Designed and engineered distributed modules for candidate signing, distribution, and validation, coordinating with cross-functional teams to ensure correctness, performance, and alignment with protocol specifications.}
      \end{cvitems}
    }

    \cventry
    {Senior Blockchain Engineer - Crosschain Bridging}
    {ChainSafe Systems - \href{https://buildwithsygma.com}{Sygma}(Decentralized Crosschain Bridging EVM-Polkadot)}
    {Global}
    {Jul. 2021 - Mar. 2025}
    {
      \begin{cvitems}
        \item {Tech Stack: Rust, EVM, Polkadot-Substrate Pallet, Multi Party Computation, ECDSA verifier, Runtime Development}
        \item {Led development of a cross-chain bridging protocol connecting multiple blockchain networks such as EVM and Polkadot, driving design, implementation, and deployment of core bridge components.}
        \item {Engineered backend modules for runtime integration, cross-ecosystem interoperability, and relayer communication.}
        \item {Owned end-to-end mainnet and testnet bridge deployment, configuration, and execution.}
        \item {Built scalable onboarding processes for new networks, ensuring reliability, performance, and seamless interoperability.}
        \item {Collaborated with cross-functional teams to align protocol design with production requirements and multi-chain standards.}
      \end{cvitems}
    }

    % \cventry
    % {Team Lead - Engineer Management}
    % {ChainSafe Systems - Ethermint and Cosmos Module for Chainlink(Cosmos)}
    % {Global}
    % {Aug. 2021 - Nov, 2022}
    % {
    %   \begin{cvitems}
    %     \item {Lead the development work on Cosmos-Chainlink module(Detail is in Project section).}
    %     \item {Designed the architecture and facilitate knowledge transferrring across the organization.}
    %     \item {Progress reporting to C level stakeholders.}
    %     \item {Team management. Facilitate 1 on 1 meetings with engineers, resource }
    %     % \item {Lead the development work on GTS(Gasless Transaction as Service)(Detail is in Project section).}
    %     % \item {Developer \& Researcher of the ChainSafe ChainBridge(Detail is in Project section).}
    %   \end{cvitems}
    % }
    
    \cventry
    {Blockchain Engineer - Protocol}
    {ChainSafe Systems - Cosmos-SDK Module for Chainlink Oracles}
    {Global}
    {Jan. 2021 - Aug. 2021}
    {
      \begin{cvitems}
        \item {Tech Stack: Go, NodeJS, Cosmos-SDK, IBC, Tendermint, Chainlink}
        \item {Developed Cosmos SDK module integrating oracle functionality, taking ownership of backend development in Go.}
        \item {Upgraded the consensus and application layers for compatibility with core blockchain protocols and virtual machine execution.}
        \item {Improved RPC interfaces to support efficient communication between the module and external services.}
        \item {Led end-to-end module development, from protocol-level implementation to testnet deployment, strengthening system design.}
      \end{cvitems}
    }
    
    \cventry
    {Blockchain Payment System Engineer}
    {BitSpawn - Deposit Manager(EVM-Solana)}
    {Toronto. ON. Canada}
    {Jul. 2019 - Dec. 2021}
    {
      \begin{cvitems}
        \item {Tech Stack: Go, NodeJS, BitCoin, Solana, Ethereum, Solidity, Etherscan-api, BlockCypher-api, ERC-20, PostgreSQL, Redis, Bloom Filter, HD wallet, KMS, BitGo, Paypal, Stripe}
        \item {Designed and implemented a blockchain payment system handling multi-token deposits, minting, and burning across chains.}
        \item {Built end-to-end backend logic, including real-time monitoring, automated processing, and production deployment on AWS.}
        \item {Enabled cross-functional teams to access reliable payment data for business decisions, acting as a core gateway for broader on-chain application logic.}
        \item {Fully responsible for system architecture, development, and operational reliability, demonstrating ownership of complex cross-chain processes.}
      \end{cvitems}
    }

    \cventry
    {Blockchain Backend Engineer}
    {OneLedger}
    {Toronto. ON. Canada}
    {Apr. 2019 - Jan. 2021}
    {
      \begin{cvitems}
        \item {Tech Stack: Go, Typescript, NodeJS, Tendermint, PBFT, LevelDB, Hierarchical Deterministic key Derivation, PostgreSQL, SQS, Linux}
        \item {Developed hierarchical deterministic (HD) wallet supporting BTC, ETH, and native chain key derivation.}
        \item {Designed and implemented user-friendly blockchain SDK, enabling developers to interact with the protocol effectively.}
        \item {Built blockchain explorer to track and visualize onchain data, improving accessibility and usability.}
        \item {Actively collaborated with the team, incorporating feedback in fast improvement cycles while strengthening design and implementation skills.}
      \end{cvitems}
    }

  \cventry
    {Blockchain Application Engineer - Dapps}
    {SkyQuark}
    {Toronto. ON. Canada}
    {Oct. 2017 - Apr. 2019}
    {
      \begin{cvitems}
        \item {Tech Stack: Ethereum, geth, parity, Solidity, Truffle, Mist, IPFS, EOS, Docker, koa framework}
    %     \item {Designed and developed Skyquark Crowdsourcing system back-end using NodeJS, MongoDB, LevelDB, web3JS, Parity}
    %     \item {Designed and developed Skyquark Aristotle Chain using Parity.}
    %     \item {Designed and developing the Aristotle token system within Edusphere eco-system.}
    %     \item {Developed Edusphere Intellectual Property protection dApp(smart contracts) on Aristotle Chain.}
    %     \item {Developed Edusphere certificate verification dApp(smart contracts) on Aristotle Chain.}
    %     \item {Designed and developed Skyquark ICO smart contract(ERC-20)}
    %     \item {Provided 'Blockchain for Junior' online lectures as instructor at www.edusphere.io}
    %     \item {Developed an EOS based PoC of Aristotle Chain prototype.}
      \end{cvitems}
    }
	

  \cventry
    {Security Platform Automation Engineer Intern}
    {BlackBerry}
    {Waterloo. ON. Canada}
    {May. 2017 - Dec. 2017}
    {
    %   \begin{cvitems}
    %     \item {Tech: Android, Jenkins, Shell Script, UiAutomatorViewer, JUnit4, Linux, Git, JIRA, SSH, Security key exchange}
    %     \item {Developed security key based unit test cases including S/MIME, PGP and large size Sign and Encrypt key.}
    %     \item {Developed test sanity to automatically build testing job for different BlackBerry app components.}
    %     \item {Set up and configure Jenkins server and nodes to organize BlackBerry security message jobs.}
    %     \item {Designed and developed Monkey command tool App for automation and pressure test on BlackBerry apps.}
    %   \end{cvitems}
    }
  
%   \cventry
%     {Front-end Developer}
%     {University of Waterloo - Renison University College}
%     {Waterloo, ON}
%     {Nov. 2015 - Apr. 2016}
%     {
%       \begin{cvitems}
%         \item {Tech: Java, JavaScript, jQuery, HTML5, CSS3, Augmented Reality}
%         \item {Designed and developed an interactive web application to demonstrate the history of the relationship between Renison University College and Anglican Religion.}
%         \item {It contains three parts: a JavaScript puzzle game, an augmented Reality photo and an information tree developed by jQuery.}
%         \item {Awarded Outstanding Project by the Anglican Religion Group.}
%       \end{cvitems}
%     }
    
%   \cventry
%     {Full Stack Developer}
%     {TCSL}
%     {Tianjin, China}
%     {Feb. 2015 - Aug. 2015}
%     {
%       \begin{cvitems}
%         \item {Tech: JavaEE, JavaScript, jQuery, Struts2, Spring3, Hibernate4, Linux, Maven, Nexus, Tomcat, PostgreSQL, SVN}
%         \item {Participated in design and development the architecture and backend framework.}
%         \item {Built a local maven component server for the entire developing group.}
%         \item {Developed business components of data persistence using Hibernate.}
%         \item {Developed business transactions control unit using Spring.}
%         \item {Participated in the development of user interfaces.}
%       \end{cvitems}
%     }
    
  \cventry
    {Interal Systems Backend Engineer Intern}
    {Oracle Corporation}
    {Tianjin, China}
    {Mar. 2014 - Feb. 2015}
    {
    %   \begin{cvitems}
    %     \item {Tech: JavaEE, AJAX, jQuery, DBCP, MySQL, Tomcat, Apache Component lib, MVC, Linux, SSH, Git}
    %     \item {Developed a social network system based on JavaEE(SSH framework) and MySQL.}
    %     \item {Designed the database and implemented with PowerDesigner.}
    %     \item {Designed the architecture and using MVC for implementation.}
    %     \item {Awarded Best Intern Project by Oracle.}
    %   \end{cvitems} 
    }
\end{cventries}
