\cvsection{Projects(Github)}
\begin{cventries}
\cventry
    {Technologies: \quad Go, Ethereum, Solidity, Cryptography, LevelDB, Oracle}
    {ChainSafe Systems - ChainBridge}
    {}
    {Feb. 2022 - Now}
    {
      \begin{cvitems}
        \item {ChainSafe ChainBridge is a decentralized cross-chain messaging protocol. It currently supports ERC20, ERC721 and generic message between any EVM based chain.}
        \item {Participated as researcher \& dev in this project.}
        \item {Mainly in charge of the Dynamic fee feature, which is another independent service to connect with chain oracle and provide the gas price and token price for the destination chain as reference to the cross-chain messaging request; It also contact he fee handler contract to preform fee calcuation.}
        \item {Also working on the research for bringing Cosmos ecosystem into the project by Cosmos ComsWasm.}
      \end{cvitems}
    }

\cventry
    {Technologies: \quad Go, Ethereum, Solidity, Open Zeppelin Relayer}
    {ChainSafe Systems - Gasless Transaction as Service}
    {}
    {Nov. 2021 - Feb. 2022}
    {
      \begin{cvitems}
        \item {GTS is a centralized server, which is able to pay gas fee on behalf of the signer of a transaction on EVM based chain.}
        \item {Participated as TL \& dev in this project.}
        \item {Currently support 3 types of transactions: Sending Ether, ERC-20, ERC-721 token transfer, arbitrary contract call.}
        \item {Powered by Open Zeppelin Relayer on the backend.}
      \end{cvitems}
    }

\cventry
    {Technologies: \quad Go, Cosmos-SDK, Chainlink}
    {ChainSafe Systems - Cosmos Chainlink Module}
    {}
    {Mar. 2021 - Nov. 2021}
    {
      \begin{cvitems}
        \item {Cosmos Chainlink module is one of the Cosmos SDK modules that designed and developed by ChainSafe Systems.}
        \item {Participated as TL \& dev in this project.}
        \item {This module follows Cosmos Module development standard.}
        \item {It links Cosmos and Chainlink ecosystems so that community developers are able to submit/retrieve the feed data from Chainlink in the Cosmos ecosystem.}
        \item {Hierarchical management design makes sure the validity of the oracle data. Each data feed maintains its own owner list and data provider list.}
        \item {Token rewarded to the valid data provider each round.}
        \item {Business agnostic design makes the module generic in any kind data.}
      \end{cvitems}
    }
    
\cventry
    {Technologies: \quad Go, Ethereum, Cosmos}
    {ChainSafe Systems - Ethermint}
    {}
    {Jan. 2021 - Mar. 2021}
    {
      \begin{cvitems}
        \item {Ethermint is a blockchain protocol developed in Go that enables Solidity on Cosmos which combines the smart contract ability of Ethereum with the fast finality and cheaper gas of Cosmos.}
        \item {Developed the gRPC and JSON-RPC layer for Ethermint. It is compatible with Web3js so that any dApps using web3js can be connected to Ethermint seamlessly.}
      \end{cvitems}
    }
    
\cventry
    {Technologies: \quad Go, NodeJS, Redis, PostgreSQL, Bloom Filter, HD wallet, FSM, Ethereum, BitCoin, Solana}
    {BitSpawn - Deposit Manager}
    {}
    {Jul. 2019 - Dec. 2021}
    {
      \begin{cvitems}
      \item {Designed and implemented Deposit Manager(Golang+NodeJS) centralized server which is the Bitspawn Payment Gateway that \\
      1.) accepts deposit by multiple currencies(ETH/BTC/ERC20 tokens/SPL tokens/USD) and mint SPWN token on internal POA network; \\
      2.) allow withdraw from SPWN token to multiple currencies(ETH/BTC/ERC20 tokens/SPL tokens/USD); \\
      3.) Providing real time currency exchange rate query, internal token conversion .etc APIs for other backend services.}
        \item {Cobra CLI: support side features other then deposit/withdraw: token migration; KMS encryption/decryption; admin mint/burn/transfer; smart contract deployment; HD wallet management and Production tx scanning and reporting.}
        \item {Support multiple platforms withdraw for one currency.}
        \item {Down time catching up for all missed blocks/transactions.}
        \item {Highly configurable: easily switch ON/OFF for deposit/withdraw currency availability, and support auto or manual process.}
        \item {Finite State Machine design allows future scaliability.}
        \item {Admin customizable Solidity smart contracts ensure the atomicity of both deposit and withdraw transactions.}  
        \item {This whole project was implemented by myself, currently has approximately 170,000 active users(By Jan 2022).}
      \end{cvitems}
    }

\cventry
    {Technologies: \quad Go, Tendermint}
    {OneLedger - Blockchain Protocol}
    {}
    {Oct. 2019 - Dec. 2021}
    {
      \begin{cvitems}
        \item {OneLedger blockchain is one of the public Blockchain networks which aims to build enterprise level Interoperability and open source for community to build dApps. (\url{https://github.com/Oneledger/protocol}).}
        \item {Using Tendermint as core consensus engine, OneLedger chain has application(node) layer, RPC layer, transaction verification /distribution layer and chain state distributed database(LevelDB) layer on fullnode and validator node.}
        \item {RPC layer: designed and implemented RPC endpoints for transaction and query.}
        \item {Transaction layer: designed and implemented transaction verification(signature mapping) for all transaction types, transaction fee charge logic, fee collection and reward withdrawal for validators.}
        \item {Distributed Database layer: designed and implemented database schema and store structure for different transaction types and block info.}
        \item {Block scope: designed and implemented block beginner and block end for internal transaction logic.}
        \item {Transactions: OneLedger Domain Service, Governance, Staking\&Delegation, Block Rewards, Multi-currency Transfer, ETH/OLT Interoperability.}
      \end{cvitems}
    }
    
\cventry
    {Technologies: \quad BitCoin, Ethereum, Typescript, BIP-32, BIP-39, Ed25519, Secp256K1, RIPEMD160, SHA256}
    {OneLedger - Hierarchical Deterministic(HD) Wallet}
    {}
    {Jun. 2019 - Apr, 2020}
    {
      \begin{cvitems}
        \item {OneLedger HD Wallet is a JavaScript module that provides ability to generate keypairs and sign Raw Transactions for multiple chains.}
        \item {Support configurable entropy to derive master seed.}
        \item {Support whole wallet backup and recovery from any device by mnemonic.}
        \item {Support BTC, ETH and OLT(OneLedger) keys derivation, address verification and transaction signing.}
        \item {Hide derived master seed and all private key to maximum security.}
        \item {Using hardened extended key path from BIP-39.}
        \item {Easily extendable to support other blockchain key algorithm.}
      \end{cvitems}
    }

\cventry
    {Technologies: \quad Typescript, NodeJS, RPC}
    {OneLedger - SDK}
    {}
    {Apr. 2019 - Jan. 2021}
    {
      \begin{cvitems}
        \item {OneLedger SDK is a whole middle layer of JavaScript modules between community developers and OneLedger blockchain protocol which allows developers to query block or transaction info and securely serialise transactions offline and broadcast them.}
        \item {Highly configurable offline transaction serialization and signing workflow which allows community to extend their own transaction types, even using different network.}
        \item {Support different types of transaction broadcasting such as Async, Sync.}
        \item {Support both regular transaction and BTC/ETH Interoperability transaction.}
        \item {Multiple sub-modules design that separates transaction preparation, signing and broadcast into different modules for scaliability.}
        \item {Easily configurable error handler for community to add and handle new errors.}
        \item {Configurable storage usage for different platforms(Web/Chrome Extension/Electron/Native).}
        \item {Support Ledger Device(Cold Wallet) with different connection type such as Bluetooth, USB etc.}
      \end{cvitems}
    }
    
    \cventry
    {Technologies: \quad Go, WebSocket, Tendermint, Tendermint Events, PostgreSQL, SQS, CronJob}
    {OneLedger - Blockchain Explorer}
    {}
    {Jun. 2019 - Jan. 2021}
    {
      \begin{cvitems}
        \item {OneLedger blockchain Explorer is a set of services that watch, synchronize new block from OneLedger blockchain; persist block/transaction data into postgreSQL database; provide restful APIs for querying; send configruable notification for blockchain data alert.(\url{https://oneledger.network})}
        \item {Self-catch-up plus SQS design guarantees the data integrity if Explorer or blockchain node is down or restarted.}
        \item {Micro-services design that data source is writing to SQS, and data handler is reading from SQS.}
        \item {Internal cronjob(goroutines) module maintains the public metrics data.}
        \item {Configurable notification module sends alerts to multiple receivers.}
        \item {Easily extendable transaction type design and DB design for new transaction types.}
        \item {Provide web socket for real-time blockchain info.}
        \item {Provide APIs for community developers to query blocks and transactions info.}
      \end{cvitems}
    }

\cventry
    {Technologies: \quad Truffle, Parity, AWS}
    {SkyQuark - Aristotle Chain}
    {}
    {May. 2018 - Apr. 2019}
    {
      \begin{cvitems}
        \item {Aristotle Chain using parity with PoA consensus algorithm generates an EVM based public chain for the foundation of SkyQuark Eco-system.}
        \item {Users need to sign up Edusphere system to get a wallet address connecting to Aristotle Chain.}
        \item {ETH Pre-fund accounts are transaction validators who are responsible for mining new blocks, validating all transactions.}
        \item {Users could be part of validators and sync full Aristotle Chain blocks to earn more tokens.}
      \end{cvitems}
    }
    
\cventry
    {Technologies: \quad Nodejs, KoA, MongoDB, LevelDB, web3.js, truffle, AWS, Postman
    }
    {SkyQuark - Crowdsourcing System}
    {}
    {Sept. 2018 - Apr. 2019}
    {
      \begin{cvitems}
        \item {Crowdsourcing system is the extension of Nodejs back-end web server between Edusphere system and Aristotle Chain.}
        \item {It's also the Aristotle chain user address, chain nodes and smart contracts   management center.}
        \item {It connects with MongoDB as main business logic database and LevelDB as users reputation and other behaviors databases.}
        \item {It communicates with Aristotle Chain through Web3.js API.}
        \item {It provides APIs to the front-end edusphere system.}
        \item {It provides users a revenue auto-distribution system based on the Aristotle Token mechanism without signing any paper or electrical revenue sharing contracts}
        \item {Users behaviors on edusphere.io will be used to calculate the reputation and token rewards and the smart contracts deployed on Aristotle Chain will be triggered to make reward transactions}
      \end{cvitems}
    }

%   \cventry
%     {Technologies: \quad Solidity, Truffle, Remix IDE, Ethereum Wallet, OpenZeppelin, Quantstamp
%     }
%     {SkyQuark ICO Smart Contract for Aristotle Token}
%     {}
%     {Aug. 2018 - Oct. 2018}
%     {
%       \begin{cvitems} 
%         \item {This ICO smart contract has four components: Secure math, ownership control, pause, ERC-20 implementation.}
%         \item {It has been tested by OpenZeppelin and Quantstamp.}
%         \item {It was deployed on Ethereum mainnet but tested on Rinkeby.}
%         \item {Aristotle Token is able to be transferred between Ethereum mainnet and Aristotle chain using parity bridge protocol(developing).}
%       \end{cvitems}
%     }

 
  \cventry
    {Technologies: \quad Truffle, Solidity, Web3, NodeJs, IPFS, Webpack
    }
    {SkyQuark - Intellectual Property Protection dApp}
    {}
    {Jun. 2018 - Sept. 2018}
    {
      \begin{cvitems}
        \item {IP Protection dApp developed on Rinkeby testnet first and deployed to Aristotle Chain after.}
        \item {It has four different layers: chain layer, smart contract layer, web3(NodeJs) layer and UI layer}
        \item {For the web part, it needs a web server like AWS to host the all front-end resource files(or IPFS) and web3 will connect to blockchain provider to interact with smart contracts and send transactions to the chain.}
        \item {For all large size documents that users submit, they are all stored on the IPFS, only hash value will be stored into blockchain.}
      \end{cvitems}
    }

  \cventry
    {Technologies: \quad Android, adb shell monkey, Android system permission, Android system sign, Git}
    {BlackBerry - Monkey}
    {}
    {Jun. 2017 - Sept. 2017}
    {
      \begin{cvitems}
        \item {This is an Android application for BlackBerry Spark Day.}
        \item {This app encapsulates adb shell monkey command for BlackBerry internal pressure and performance testing.}
        \item {Granting Android system permission and system sign to run sudo commands.}
        \item {Running monkey command on target apps and generating the testing report for analyzing.}
      \end{cvitems}
    }
  
  \cventry
    {Technologies: \quad Android, Google Map API, Geolocation, AWS, MySQL, Web Server, Git}
    {UWaterloo Hackathon - Waterloo Discovery}
    {}
    {Feb. 2017 - Feb. 2017}
    {
      \begin{cvitems}
        \item {Developed an Android application about exploring the city of Waterloo for new comers such as international students and travelers in 2 people's team.}
        \item {Using Google Map API to locate users, then calculate the distance.}
        \item {Using Google Nearby resources.}
        \item {Awarded Top 5 Hackathon project.}
      \end{cvitems}
    }
    
    % \cventry
    % {Technologies: \quad Android, WebSocket, Multi-threading, Concurrency, MySQL, Git}
    % {Instant Message system}
    % {}
    % {Oct. 2016 - Jan. 2017}
    % {
    %   \begin{cvitems}
    %     \item {Developed an IM Android application for users to join in groups and chat.}
    %     \item {Developed both client and server. The service was built on WebSocket.}
    %   \end{cvitems}
    % }
    
    % \cventry
    % {Technologies: \quad JavaEE, Struts2, Spring3, Hibernate4, Maven, Nexus, Tomcat, MySQL, Design patterns, MVC, Git}
    % {FreeX(Backend)}
    % {}
    % {Oct. 2016 - Dec. 2016}
    % {
    %   \begin{cvitems}
    %     \item {Designed the architecture and developed the web server based on JavaEE for currency exchange Android App.}
    %     \item {Using Factory pattern and Abstract Data Access Object class in Data persistence layer to improve scalability.}
    %     \item {Using transaction management in Spring to ensure atomicity of each transaction.}
    %     \item {Using Session to identify clients and JSON to communicate with clients.}
    %     \item {Designed the database.}
    %   \end{cvitems}
    % }
    
    % \cventry
    % {Technologies: \quad JavaEE, Servlet, DBCP, Java 2D Graphics, Tomcat, MySQL}
    % {Hospital Invoice printing System}
    % {}
    % {Sept. 2016 - Oct. 2016}
    % {
    %   \begin{cvitems}
    %     \item {Designed and developed a web server system based on JavaEE(Servlet, JDBC, Java 2D Graphics) for hospital invoice printing System.}
    %     \item {Using Servlet to distribute requests and responses.}
    %     \item {Using JDBC to persist data into MySQL Database.}
    %     \item {Using Java 2D Graphics API to print out the data in a changeable format}
    %     \item {Using JavaScript and jQuery to develop the frontend for searching, sorting and modifying data}
    %     \item {Designed the database.}
    %   \end{cvitems}
    % }
    
    %  \cventry
    % {Technologies: \quad  Android, SQLite}
    % {Multiple Choice}
    % {}
    % {Aug. 2016 - Oct. 2016}
    % {
    %   \begin{cvitems}
    %     \item {Developed an application to simulate the question asking and answering.}
    %     \item {Two user scenarios for question asking and question answering.}
    %     \item {Timer limited for answering questions and multi-threading controlling.}
    %     \item {Question history system could record each user's behavior and make a ranking}
    %   \end{cvitems}
    % }
    
    % \cventry
    % {Technologies:\quad JavaEE, MVC, Struts2, Hibernate4, Spring-IoC, MySQL, Tomcat, Apache components, AJAX, JavaScript, jQuery, JSP, HTML, CSS, Bootstrap}
    % {Cookie Social Network System }
    % {}
    % {Dec. 2014 - Jun. 2015}
    % {
    %   \begin{cvitems}
    %     \item {Developed a social network system based on JavaEE.}
    %     \item {This project contains several components such as book, music, activity, goods.}
    %     \item {Users are able to follow each other and share different info. They could also make comments just like Facebook}
    %     \item {Designed the database structure and architecture, using SSH frameworks to enhance MVC, Spring was using for Ioc.}
    %     \item {Awarded the Top project scholarship from the Government.}
    %   \end{cvitems}
    % }
    
\end{cventries}
